---
title: "Searchable Table of Species"
date: "`r Sys.Date()`"
output:   
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
---

[Return to Main](https://vandenbergrf.github.io/EthogramArchive/)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(DT)
library(dplyr)
SpeciesList = read_csv("SpeciesList.csv")
```


# The Searchable Table

Below you will find a table of the species currently in the system. 
To suggest an update, please specify which name changes (if any) and movements between different branches (if any) should be performed. Looking at you, bat phylogenists.
If your preferred genus/family/order/kingdom/etc. is not on this page yet, put in a request! For convenience, the branches will be built bottom-up. So there won't be a page for felids until we have at least one page at species level.

## Table

```{r, echo=F}

SpeciesList$Page_Link = paste("<a href='",SpeciesList$Page_Link,"'>",SpeciesList$Species,"</a>",sep="")
SpeciesList$Ethograms_In_Genus = NA
Temp = SpeciesList %>% group_by(Genus) %>% summarise(Ethograms=sum(Number_Of_Ethograms))
for(i in 1:nrow(Temp)){
  SpeciesList$Ethograms_In_Genus[SpeciesList$Genus==Temp$Genus[i]] = Temp$Ethograms[i]
}
rm(Temp)

datatable(SpeciesList, escape=5)

```


